\documentclass{article}

\usepackage{tabu}
\begin{document}

\title{CRI11Annex – Checklist for communications}

\maketitle





 


\begin{tabu} to \textwidth { |X|X|X| }
\hline



\emph{\textbf{Topic?}} & \emph{\textbf{Title:}} & \emph{\textbf{Communications}}
 \\


Target group:  &  & Date:
 \\
\hline

\end{tabu}

 


\subsubsection{Selecting the form of communication}\label{H3683887}



☐   Press release


☐   Press conference/expert interview


☐   Hotline


☐   FAQs


☐   Website of the administrative unit


☐   Social media (e.g. Twitter, Instagram) 


\subsubsection{Content-related preparation }\label{H351953}



☐   What is the current situation?


☐   What has happened, when and where?


☐   What damage has been caused?


☐   How many people (number) are affected?


☐   How is a situation likely to develop? Best case vs. worst case


☐   What action has been taken so far by the authorities?


☐   What are the authorities planning to do? Activities?


☐   Who will be affected? What (behavioural) rules follow as a result of the incident?


☐   What specialist information is relevant?


☐   What information do regional/national bodies have in reserve?


☐   What easy-to-understand information is relevant? 


☐   What are the most important messages for the general public?


\subsubsection{Press release}\label{H7689813}



☐   What? When? Where? Who? 


☐   Contact person 


☐   Date, time if known


☐   Website, social media, further information and contact data if available 


☐   Press spokesperson


☐   Other competent contacts, e.g. fire service, police, (higher) public health authorities, senate department





\subsection{Checklist – press conference}\label{H59697}



(based on preliminary work by Christoph Lang, former Director of the Press Office, Senate Department for Health and Equality)


\subsubsection{Invitation}\label{H6901633}



☐   Specified time, location and duration 


☐   Support for media representatives (possibly on site)


☐   Designate room for individual interviews (radio, podcasts, television)


☐   Prepare press folder


☐   Specify briefed interview partners


☐   Determine telephone availability  


\subsubsection{Cordons/restrictions on access}\label{H5004432}



 ☐   Briefing for security services


\subsubsection{Press room}\label{H3108982}



☐   Catering (e.g. beverages, snacks, for example sandwiches)


☐   Work facilities: chairs and desks


☐   Some power outlets (provide multi-sockets if needed) for charging smartphones and notebooks


☐   Ideally also WLAN (provide access codes if necessary)


☐   Prepare screens/pinboards and flipcharts


☐   Specify TV-appropriate background for interviews


\subsubsection{Support for journalists}\label{H6595140}



☐   Trained officer (press spokesperson) permanently available


☐   Alternative -– officer permanently on call?


☐   Specify telephone availability, possibly hotline


\subsubsection{Regular press briefings}\label{H8837330}



☐   Who talks? 


☐   Are the relevant persons informed? 


☐   Media training completed?


☐   Experts on site? In contact with media representatives?


\begin{tabu} to \textwidth { |X|X|X| }
\hline



\emph{\textbf{Institution:}}   &  & \emph{\textbf{Version:}}
 \\


Prepared by:  &  & Filed under:
 \\
\hline

\end{tabu}

 

\end{document}
